---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# econres

<!-- badges: start -->
<!-- badges: end -->

The goal of `econres` is to facilitate **my** economics research by helping me to load `R` packages **I** commonly use, create descriptive plots and table presentations of time series (based on **my** aesthetic taste), and automate other tasks common for **my** economic research.   

If someone else finds `econres` useful for **their** research they are free to use it (or parts of it) as they please.

## Installation

You can install the development version of `econres` from  [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("lyuben-ivanov/econres")
```

## Example

This is a basic example which shows you how to efficiently produce an elegant times series plot that demonstrates the "hockey stick" of growth. To produce this plot you need to provide a suitably-formatted data frame (in wide format, with the first column being the time index) to the `tsr()` function and it will plot the values in the columns as time series and label them automatically with the names of the corresponding columns. Do note that after the first element is supplied to the function you can add any element that the methods of `plot()` accept to customize the plot further.

```{r example}
library(econres)

mGDP |>
dplyr::select(c(Year, `United Kingdom`, `United States`, China, India, Germany)) |>
dplyr::filter(Year >= 1000) |>
dplyr::arrange(Year) |>
tsr(xlab = 'Year', main = "The hockey stick of growth", cex.main = 1.2)

```


